Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-27 paper/structureScene.tex
add a lot of references regarding acoustic scenes classification. Add short descriptions of the dcase 2013 participant. add refList.txt (old references). Clean biblio.bib. Remove .bbl and .blg

Also, some recent works demonstrate the interest of such approaches for the characterization of human acoustic pleasantness in urban areas \cite{lafay, lavandier} and the prediction of annoyance due to the traffic \cite{gloaguen}. We believe that those case study are of interest for the signal processing community as they have strong societal impacts and raises interesting research avenues. Unfortunately, those fields of research are still in infancy and consequently very few well built datasets are available for evaluation purposes.

A closely related field of investigation that is relatively more mature is the classification of acoustic scenes whose aim is to predict labels by processing audio data. Despite its lower value, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois} and been considered in the data processing field for a while, with availability of some well designed evaluation datasets.

@@

GL 1

ML 2

\subsection{Goal}

\subsection{Methods}

@@

dcase2013 \cite{7100934} \cite{giannoulis2013database}

>>>>

Also, some recent works demonstrate the interest of such approaches for the characterization of human acoustic pleasantness in urban areas \cite{lafayPartI, guyot2005urban, ricciardi2015sound} \gl{What was the lavandier article ?} and the prediction of annoyance due to the traffic \cite{gloaguen}. We believe that those case study are of interest for the signal processing community as they have strong societal impacts and raises interesting research avenues. Unfortunately, those fields of research are still in infancy and consequently very few well built datasets are available for evaluation purposes.

A closely related field of investigation that is relatively more mature is the classification of acoustic scenes whose aim is to predict labels by processing audio data. Despite its lower value, it has the advantage of being rooted by numerous works in cognitive psychology on categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and been considered in the data processing field for a while, with availability of some well designed evaluation datasets.

@@

\gl{bag of frame approach:} \cite{aucouturier2007bag}: bag of frame approach. \cite{lagrange:hal-01082501}: why the bag of frame approach does no work. \\

\gl{DCASE challenge:} \cite{chum2013ieee}: CHR system, using HMM and frame based classification. \cite{elizalde2013vector} ELF system, I vector approach using probabilistic LDA as classifier. \cite{geiger2013large} GSR system, basically mel/MFCC using SVM as classifier. \cite{krijnders2013tone} KH system, tone fit features computed from cochleogram (but similar results are obtained with MFCCs) using SVM as classifier. \cite{li2013auditory} LTT system, Tree bagger classifier used on segments (MFCCs) prior to a majority vote. \cite{lee2013acoustic} NHL system, unsupervised feature learning approach on mel frequency spectrogram with selective Max-pooling. Supervised training is performed using SVM. \cite{nogueira2013sound} NR1 system, MFCC and spatial features (inter-aural differences) with SVM as classifier. \cite{olivetti2013wonder} OE system, normalized compression distance (I honestly did not understand a thing about it, but this the worst method of the challenge anyway) using  Random Forest  classifier.  \cite{patil2013multiresolution} PE system, 2D Gabor filters applied on 1sec segments with SVM as classifier.  \cite{rakotomamonjy2015histogram} RG system, histogram of gradient representation, computed from a constant Q transform with SVM as classifier.  \cite{roma2013recurrence} RNH system, RQA stacked with MFCC, SVM as classifier. \\

\gl{Other paper:} \cite{jiang2005svm, kalinli2009saliency, su2011environmental, barchiesi2015acoustic, ye2015acoustic, bisot2015hog, chakrabarty2015exploring, xue2015auditory, bisot2016acoustic}

\subsection{Describing a scene (Feature extraction)}

\subsection{Classifying a scene}

@@

DCASE 2013 challenge reference papers. \cite{giannoulis2013database, 7100934} \\
